Influence of Connectivity on Dung Beetle Communities

### 2025-04-22 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
p1

Paragraph 1: Overall Topic & Why it is interesting and Important.     
  As human disturbances continue to expand into natural landscapes, intact habitats are becoming increasingly fragmented. Effects from isolation can vary, however as habitats are broken down community structures are significantly altered [@WOS:000419965700012]. This degradation of structure lends to loss in biodiversity on a global scale and interruptions in ecosystem processes and functions [@haddad_habitat_2015].

Like many ecological processes, fragmentation is a complex and multifaceted phenomenon

>>>>

Paragraph 1: Overall Topic & Why it is interesting and Important.

  As human disturbances continue to expand into natural landscapes, intact habitats are becoming increasingly fragmented. Like many ecological processes, fragmentation is a complex and multifaceted phenomenon bringing about many consequences which can be both positive and negative for ecosystems [@fahrig_effects_2003] [@fletcher_is_2018]. However, as habitats are broken down community structures are significantly altered [@WOS:000419965700012]. This alteration of structure typically lends to loss in biodiversity on a global scale and interruptions in ecosystem processes and functions [@haddad_habitat_2015]. Researchers today continue to search for strategies to mitigate the negative effects resulting from changes in landscape structure [@noh_forest_2022].
